---
title: "Forth-Activity-1"
author: "Tessa Forth"
date: "2026-09-28"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***

# Main Research Interests
My principal areas of interest include:

- Tropical and coastal ecology

- Spatial analysis/remote sensing/GIS

- Carbon sequestration

At McMaster, I work with Dr. Alemu Gonsamo's _Remote Sensing Lab._ My research here centers on **how tropical forests recover their biomass following stand-replacing disturbances.** My approach uses _space-for-time substitution,_ which means I quantify biomass from one recent year, but across forests that were disturbed in different years. That way, I can find a relationship between forest age and biomass, essentially finding the rate of recovery over time.

Specifically, I am recording aboveground biomass estimations from spaceborne LiDAR data, made available by the _GEDI L4A_ product, and relating this to forest loss data from the _Global Forest Change_ project.

***

# Favorites

## Favorite Music
1. Spring Is Coming With A Strawberry In The Mouth: Roger Doyle & The Operating Theater
2. Those Eyes, That Mouth: Cocteau Twins
3. Hello Earth: Kate Bush
4. The Predatory Wasp Of The Palisades Is Out To Get Us!: Sufjan Stevens
5. Behind The Wheel: Depeche Mode

## Favorite Equation
_NDMI = (NIR-SWIR) / (NIR+SWIR)_

Where _NDMI_ is the Normalized Difference Moisture Index, _NIR_ is near infrared reflectance, and _SWIR_ is shortwave infrared reflectance.

## Favorite Artists
Name | Achievements
- | -
John Nelson | A cartographer who makes beautiful maps and tutorials. My favorite is an animated map of the world's oceans using the unique Spilhaus projection.
J.R.R. Tolkien | The author of the renowned fantasy trilogy "The Lord of The Rings," as well as "The Hobbit" and "The Silmarillion."
Michelangelo | Famous for painting the ceiling of the Sistine Chapel, as well as iconic sculptures such as the Pieta and David.
Francisco Goya | Known for expressive and thought-provoking paintings such as "The Third of May 1808" and "Saturn Devouring His Son."
Pierre-Auguste Renoir | A French impressionist painter with works such as "Luncheon of the Boating Party" and "The Umbrellas."


# A Chunk of Code
```{r}
# Print the traditional first line of code, but adapted slightly to match a Kate Bush song title!
print("Hello Earth")

# Calculate the first 5 powers of my favorite number
favoritenumber <- 4
powers <- favoritenumber^(1:5)
print(powers)
```

